Condensed Matter Field Theory notes

### 2017-03-04 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] Sth. trivial about imaginary time. (I don't know why this modification is not included in the previous commit)

\section{Eq. 3.5}

>>>>

\section{About \texorpdfstring{$\dot{q}$}{} and imaginary time}

The $\dot{q}$ in all the path integrals, especially eq.3.6 and eq.3.8, is in
fact a shorthand for the divided difference $\frac{q_{n+1}-q_n}{\Delta t}$ as in
pp.99 (the buttom). It is not exactly the same as $\dot{q}$. pp.343 of
\cite{Greiner1996} also mentioned that in this sense, the Lagrangian in all
path integrals is not identical with the ordinary Lagrange function. Though, I
still do not know if this matters at all.

In the most common imaginary time transformation, such as those mentioned in
pp.106 of \cite{Altland2010}, and pp.358 of \cite{Greiner1996}, we have the
transformation $t\to -i\tau$. This in effect change all the $\Delta t$ in, e.g.
eq 3.5 (pp.99) of \cite{Altland2010}, to $-i\Delta\tau$. Therefore, the divided
difference
$$ \frac{q_{n+1}-q_n}{\Delta t} \to \frac{q_{n+1}-q_n}{-i \Delta\tau}$$
Therefore,
$$ \dot{q} \to i\partial_\tau q $$
$$ \dot{q}^2 \to -\partial^2_\tau q $$
\section{Eq. 3.5}
